Turchin's method of statistical regularization

### 2018-02-27 AYSS-2017/article/ayss2017-Zeleniy.tex
Be more clear about method's features
- "Define errors of obtained solution" is ungrammatical
- "Don't contain undefined parameter" is cryptic on top of
   it

Solving such ill-possed problems requires additional operation called regularization. Regularization is a process of introducing additional information for transition from ill-possed problem to well-possed problem. The idea of statistical regularization~\cite{Turchin, Turovceva} is to look on the problem from the point of view of Bayessian statistics approach: unknown statistical value $\varphi(x)$ could be reconstructed using  measured value $f(y)$, the model ($K(x,y)$) and some prior information about $\varphi(x)$ behavior. Main features of statistical regularization:
\begin{itemize}
    \item Based on Bayesian approach and decision theory (choice theory).
    \item Consider different a prior information: smoothness, non-negatives, etc.
    \item Define errors of obtained solution.
    \item Don't contain undefined parameter.
\end{itemize}

>>>>

Solving such ill-possed problems requires additional operation called regularization. Regularization is a process of introducing additional information for transition from ill-possed problem to well-possed problem. The idea of statistical regularization~\cite{Turchin, Turovceva} is to look on the problem from the point of view of Bayessian statistics approach: unknown statistical value $\varphi(x)$ could be reconstructed using  measured value $f(y)$, the model ($K(x,y)$) and some prior information about $\varphi(x)$ behavior. Main features of statistical regularization:
\begin{itemize}
    \item Based on Bayesian approach and decision theory (choice theory).
    \item It's able to accommodate various forms of prior information, such as
      smoothness, constraints on boundary conditions, non-negativity, etc.
    \item It allows estimation of errors for reconstructed function $\phi$
    \item Gives clear data-driven procedure for choice of regularization
      strength.
\end{itemize}
